Filling in the Gaps: Using Consumer Products to Replace Missing Pollution Data

### 2022-03-07 paper/15min-presentation/15min-presentation.tex
Updates from Overleaf

%---------------------------------------------------------
%Purple Air Outdoor Monitors
\begin{frame}
\frametitle{Purple Air Outdoor Monitors}
\includegraphics[width=0.48\textwidth]{output/figures/pa/all_ca_and_15_pa_monitors.png}
\includegraphics[width=0.48]{0500}
\end{frame}
%---------------------------------------------------------

>>>>

%---------------------------------------------------------
%Purple Air Outdoor Monitors
\begin{frame}
\frametitle{Purple Air Outdoor Monitors}
\hspace{1em}
Purple Air Sensors in California 
\hspace{4em}
LA Site Example \\

\includegraphics[width=0.49\textwidth]{output/figures/pa/all_ca_and_15_pa_monitors.png}
\includegraphics[width=0.49\textwidth]{output/figures/concentric_ranges/county-037_site-4004_epa-pa-concentric-ranges.png}
\end{frame}
%---------------------------------------------------------
